

% -----------------------------------------------------------------

%TC:ignore



\section{Conflict of Interest Statement}
%All financial, commercial or other relationships that might be perceived by the academic community as representing a potential conflict of interest must be disclosed. If no such relationship exists, authors will be asked to confirm the following statement: 

The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.

\section{Author Contributions}

G.H-P. wrote the Eirene code. L.L. and C.T. wrote the rest of the code and performed all experiments. L.L. created all figures and tables. G.H-P. and L.Z. designed, directed, and supervised the project. G.H-P. developed the theory in the Supplementary Material. All authors contributed to the analysis of the results and to the writing of the manuscript.

\section{Funding}
This material is based upon work supported by the National Science Foundation under grants no. DMS-1854683, DMS-1854703, and DMS-1854748. 

\section{Acknowledgments}
%This is a short text to acknowledge the contributions of specific colleagues, institutions, or agencies that aided the efforts of the authors.
The authors are grateful to David Turner for helpful advice on selection of linear solvers. They also thank and acknowledge the initial work done by Robert Angarone and Sophia Wiedemann on this study.


\section{Supplemental Data}

Details regarding implementation and proofs of correctness for the algorithms discussed in \se \ref{sec:programsandmethods} as well as an additional figure and table may be found in the Supplementary Material.

% \href{http://home.frontiersin.org/about/author-guidelines#SupplementaryMaterial}{Supplementary Material} should be uploaded separately on submission, if there are Supplementary Figures, please include the caption in the same file as the figure. LaTeX Supplementary Material templates can be found in the Frontiers LaTeX folder.

\section{Data Availability Statement}
The data sets and code for this study can be found in the repository \cite{li_thompson}.

\bibliographystyle{formatting_stuff/frontiersinHLTH&FPHY} % for Science, Engineering and Humanities and Social Sciences articles, for Humanities and Social Sciences articles please include page numbers in the in-text citations
%\bibliographystyle{frontiersinHLTH&FPHY} % for Health, Physics and Mathematics articles
\bibliography{test}

%%% Make sure to upload the bib file along with the tex file and PDF
%%% Please see the test.bib file for some examples of references

%TC:endignore